Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-14 main.tex
More rearrangement

\subsection{Contours and Variants}

Intuitively, we use the word {\em policy} for any kind of dynamic
enforcement mechanism (e.g., a runtime taint tracker, heap coloring rules,
capability hardware, etc.). We use {\em property} for a mathematical
predicate on programs (i.e., machine states) articulating some useful
security goal, e.g. noninterference. \iftext\bcp{Not quite true, if we stick
  with hyperproperties.} \fi

@@

Given a machine state $\mach$ and a contour $\contour$, a {\em variant} of
$\mach$ with respect to $\contour$ is any machine state $\mach'$ whose
components agree with $\mach$ on all components marked $\LOW$ by
$\contour$---i.e., if $\contour(\component) = (\LOW$,\,\underscore), then
$\mach(\component) = \mach'(\component)$.  \bcp{Move this to the NI section.}

@@

@@

\bcp{Maybe make it a sequence of maps from components to values?  This is
  simpler, but it means we can ``observe the observbility of locations...''
But is this too unrealistic?}

@@

A {\em contoured hyperproperty} is a set of pairs of contoured
traces\iftext{} \bcp{Maybe prefix closed?}\fi.
\bcp{Should we require that it contain all possible starting states and
  contours (though of course the sequences can be singletons in many
  cases!)?  What does it mean if it doesn't?}

@@

>>>>

\subsection{Contours}

\iftext
Intuitively, we use the word {\em policy} for any kind of dynamic
enforcement mechanism (e.g., a runtime taint tracker, heap coloring rules,
capability hardware, etc.). We use {\em property} for a mathematical
predicate on programs (i.e., machine states) articulating some useful
security goal, e.g. noninterference. \iftext\bcp{Not quite true, if we stick
  with hyperproperties.} \fi
\fi

\bcp{Idea: Remove the HIGH/LOW part from contours and instead make it part
  of the $X$ parameter to both properties and policies.  (I.e., we will have
  ``X properties'' and ``X policies'' for each X.)}

@@

@@

\bcp{Try it the other way round: a sequence of maps from components to
  values.  Need to extend values with $\bot$ for always-hidden elements.
  Emphasize that ``observability is not observable.''}
\bcp{Also, change OBS to VIS}

@@

% \bcp{Maybe make it a sequence of maps from components to values?  This is
%   simpler, but it means we can ``observe the observbility of locations...''
%   But is this too unrealistic?}

@@

A {\em contoured hyperproperty} is a set of pairs of contoured
traces\iftext{} \bcp{Maybe prefix closed?}\fi.
% \bcp{Should we require that it contain all possible starting states and
%   contours (though of course the sequences can be singletons in many
%   cases!)?  What does it mean if it doesn't?}

\bcp{Not quite enough: Policies and properties needs to know where are the
  call and return sites.  So what we should do is to talk instead about ``$X$
  policies'' (i.e., make ``policy'' a type operator) and replace the initial
  $\CONTOURS$ argument to both policies and properties by an element of
  $X$.}

@@

Given a machine state $\mach$ and a contour $\contour$, a {\em variant} of
$\mach$ with respect to $\contour$ is any machine state $\mach'$ whose
components agree with $\mach$ on all components marked $\LOW$ by
$\contour$---i.e., if $\contour(\component) = (\LOW$,\,\underscore), then
$\mach(\component) = \mach'(\component)$.
